Language-Based Low-Level MPC Security: $\metaprot$ to $\minifed$

### 2024-05-05 ppdp24/bruteforce.tex
checkpoint

As per standard nomenclature, \emph{atoms} are $\minifed$ variables $x$, \emph{literals}
are atoms or negated atoms, and clause bodies are conjunctions of literals.
A \emph{fact} is a clause with no body. A \emph{Datalog program} is a list of clauses.
$$
\begin{array}{rclr}
  \mathit{body} &::=&  x \mid \neg x \mid x \wedge \mathit{body} \mid \neg x \wedge \mathit{body} \mid \varnothing \\
  \mathit{clause} &::=& x \gets \mathit{body} \mid x \gets
\end{array}
$$

\begin{mathpar}
  \vars\ \secret{w} \cid \defeq \{ \elab{\secret{w}}{\cid} \}

@@

  \vars\ (\be_1 \exor \be_2)\ \cid \defeq (\vars\ \be_1\ \cid) \cup (\vars\ \be_2\ \cid)
\end{mathpar}

The first step in converting a protocol $\prot$ to a Datalog
program is to apply $\solve$ locally to each command
in $\prog$, obtaining constraints on memories that satisfy each
view in isolation.  
\begin{definition} Define:
$$
{vtt}(\xassign{x}{\be}{\cid}) \defeq (x, (\solve{(\mems(\vars\ \be\ \cid))}{\be}{\cid}))
$$
\end{definition}
Given this definition, the mapping of ${vtt}$ across a program
$\prog$- i.e., $(\mathit{map}\ {vtt}\ \prog)$-  essentially defines the
logic program, modulo some syntactic conversion. We can
accomplish the latter as follows, where $\datalog(\prog)$ defines the
full conversion.
\begin{definition} We define the conversion from memories to
  literals and clause bodies as follows:
\begin{mathpar}
  \logit{x \mapsto 1} = x

>>>>

We define the syntax of Datalog as follows. As per standard
nomenclature, \emph{atoms} are $\minifed$ variables $x$,
\emph{literals} are atoms or negated atoms, and clause bodies are
conjunctions of literals.  A \emph{fact} is a clause with no body. A
\emph{Datalog program} is a list of clauses.
$$
\begin{array}{rclr}
  \mathit{body} &::=&  x \mid \neg x \mid x \wedge \mathit{body} \mid \neg x \wedge \mathit{body} \mid \varnothing \\
  \mathit{clause} &::=& x \gets \mathit{body} \mid x \gets
\end{array}
$$
When translating protocols, we need to extract the variables
that occur in expressions $\be$ computed by a client $\cid$,
written $\vars\ \be\ \cid$ where:
\begin{mathpar}
  \vars\ \secret{w} \cid \defeq \{ \elab{\secret{w}}{\cid} \}

@@

  \vars\ (\be_1 \exor \be_2)\ \cid \defeq (\vars\ \be_1\ \cid) \cup (\vars\ \be_2\ \cid)
\end{mathpar}
... and so on. Then, to begin converting a protocol $\prot$ to a Datalog
we define the function ${vtt}$ that applies $\solve$ locally to each command
in $\prog$, obtaining the subset of memories that result
in a variable assignment of $1$.  
\begin{definition} Define:
$$
{vtt}(\xassign{x}{\be}{\cid}) \defeq (x, (\solve{(\mems(\vars\ \be\ \cid))}{\be}{\cid}))
$$
\end{definition}
The mapping of ${vtt}$ across a program
$\prog$- i.e., $(\mathit{map}\ {vtt}\ \prog)$-  essentially defines the
logic program, modulo some syntactic conversion. We can
accomplish the latter as follows, where $\datalog(\prog)$ defines the
full conversion.
\begin{definition} We define the conversion from memories to
  literals and clause bodies as follows:
\begin{mathpar}
  \logit{x \mapsto 1} = x
